Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-16 modelling/modelling.tex
Grammar fix

Some limitations were included in Section 3.1, where the observed data have a relative high standard deviation at certain measurement points; more measurement repeats or more measurement points could help to represent more accurate trajectories of the modelled variables and thus more possible models can be proposed. On the other hand, more accurate observed are alway beneficial to mathematical modelling, especially to complex dynamic systems.

As stated, our models are largely based on the experimental evidence from Tsarouchas et al.\cite{ref:Tsarouchas}. Some hypothesised interactions may differ from real case, and there may exist undiscovered mechanisms. These could lead to model misspecification, where the model could fit the data but with wrong interaction paths, or the model can hardly fit the data and recover some local features observed in the data.

>>>>

Some limitations were included in Section 3.1, where the observed data have a relatively high standard deviation at certain measurement points. More measurement repeats or more measurement points could help to represent more accurate trajectories of the modelled variables, and thus more possible models can be proposed. On the other hand, more accurate observed data are always beneficial to mathematical modelling, especially to complex dynamic systems.

As stated, our models are largely based on the experimental evidence from Tsarouchas et al.\cite{ref:Tsarouchas}. Some hypothesised interactions may differ from a real case, and there may exist undiscovered mechanisms. These could lead to model misspecification, where the model could fit the data but with wrong interaction paths, or the model can hardly fit the data and recover some local features observed in the data.
